TITLE

### 2024-08-23 slides.qmd
Basic website structure (paper + slides + .yml)

---
title: "The Effects of Mandatory Seat Belt Laws on Driving Behavior and Traffic Fatalities"
author:
  - name: Juan David Rengifo-Castro
    orcid: 0009-0004-5169-4484
    email: jdrengifoc@eafit.com
    affiliations:
      - name: EAFIT
        city: Medellín
  - name: Angel Samuel Suesca Rios
    email: assuescar@eafit.edu.co
    affiliations:
      - name: Banco de la República
        city: Medellín
  - name: Mario Aguirre Posada
    email: maguirrep@eafit.edu.co
    affiliations:
      - name: EAFIT
        city: Medellín
format: html
editor: visual
---

>>>>

---
title: "TITLE"
author:
  - name: Juan David Rengifo-Castro
    orcid: 0009-0004-5169-4484
    email: jdrengifoc@eafit.com
    affiliations:
      - name: EAFIT
        city: Medellín
  - name: Angel Samuel Suesca Rios
    email: assuescar@eafit.edu.co
    affiliations:
      - name: Banco de la República
        city: Medellín
  - name: Mario Aguirre Posada
    email: maguirrep@eafit.edu.co
    affiliations:
      - name: EAFIT
        city: Medellín
format: 
  revealjs:
    chalkboard: true
footer: |
  <a href="paper.html" class="home-button">Home</a>
editor: visual
---
